Invasive chameleons released from predation display more conspicuous colors

### 2021-12-02 supp.Rmd
Added new Table S6 with interaction model

# Additional Supplemental Results
## Body regions are perceived differently by predators but exhibited similar effect sizes

>>>>

```{r tableS6_new, fig.width = 8, fig.height = 1, fig.asp = 0.1136364, tab.cap = "Results of interaction models comparing luminance and chromatic contrast of Hawaiian and Kenyan lizards against a Hawaiian and Kenyan background (background = Kenya) in both social contexts (male-male competition and courtship). Model estimates (mean and contrasts), standard error (SE), degrees of freedom (df) and 95% confidence intervals (95% CI) for models were fitted using robust variance estimators to correct standard errors for non-independence, and we used Satterthwaite's degrees of freedom. Significant parameter estimates are those where the 95% CIs do not include zero. Relevant contrasts that compare Hawaiian and Kenyan populations both againts the same Kenyan background are indicated by '*'."}
source("./R/func.R")
final_S6 <-  read.csv(file = "./output/tables/tableS6.csv")

  # Table
 Tab_S6 <- flextable(final_S6) %>%  table_style6() %>% fit_to_width(max_width = 7)
 table1

```
# Additional Supplemental Results
## Body regions are perceived differently by predators but exhibited similar effect sizes
